% Curriculum vitae
% Jason A. Heppler | jason@jasonheppler.org | https://jasonheppler.org
% Updated: 2024-05-31

%%% 

\documentclass[10pt]{article}

%%%------------------------------------------------------------------------
%%% Packages 
%%%------------------------------------------------------------------------

\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry}
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
\usepackage[osf,sc]{mathpazo}
\usepackage{inconsolata}
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing
\usepackage{noto}
\usepackage[T1]{fontenc}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

\def\myauthor{Jason Heppler}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{George Mason University}
\def\myjob{Senior Web Developer}
\def\mycourtesy{Senior Web Developer}
\def\myaddress{Roy Rosenzweig Center for History and New Media}
\def\myemail{jason@jasonheppler.org}
\def\myweb{https://jasonheppler.org}
\def\myphone{+1 605 770-5871}
\def\mytwitter{jaheppler}
\def\mygithub{hepplerj}
\def\mypgp{7194 C159 B68D A2B3}

\date{} % not used (revision control instead)
\def\mykeywords{Jason, Heppler, Jason Heppler, Vita, CV, Resume, History}

% HEADINGS
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\sectionfont{\sffamily\bfseries\Large} 
\subsectionfont{\sffamily\bfseries\scshape\normalsize} 
\subsubsectionfont{\sffamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1}
\usepackage[usenames,dvipsnames]{xcolor}
% tightlist fix
\def\tightlist{}

%%%------------------------------------------------------------------------
% PDF SETUP
%%%------------------------------------------------------------------------

\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Jason A. Heppler - CV}, pdfauthor={Jason A. Heppler}]{hyperref}
\hypersetup{
  colorlinks   = true,
  allcolors    = RoyalBlue 
}

\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
\usepackage{fontawesome}

%%%------------------------------------------------------------------------
%%% Document 
%%%------------------------------------------------------------------------

\begin{document}

\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

%%%------------------------------------------------------------------------
%%% Version date
%%%------------------------------------------------------------------------

%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------

\noindent{\LARGE Jason A. Heppler}\\[-0.1in] \\
\noindent{\footnotesize \emph{short curriculum vitae}}

\vskip 0.05in

\noindent{\footnotesize \textemdash} \\
\noindent{\normalsize \myaddress} \\
\noindent{\normalsize George Mason University} \\ 
\noindent{\footnotesize \textemdash} \\

\begin{minipage}[t]{2.95in}
  \flushleft {
  \footnotesize
  4400 University Drive, MSN 1E7 \\
  \vspace{-0.05in} Fairfax, \textsc{VA} 22030}
\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{3.5in}
  \flushleft \footnotesize
  \texttt{\href{mailto:\myemail}{\myemail}} \\
  \texttt{\href{\myweb}{\myweb}} \\ 
  \texttt{\href{https://orcid.org/0000-0003-4158-6186}{0000-0003-4158-6186}} \\ 
\end{minipage}

\subsection{Education}\label{education}

\textbf{Ph.D.}, History, University of Nebraska-Lincoln (2016) \\
\textbf{M.A.}, History, University of Nebraska-Lincoln (2009) \\
\textbf{B.A.}, History, South Dakota State University (2007)

\subsection{Current Appointments}\label{Appointments}

Senior Developer-Scholar, Roy Rosenzweig Center for History and New Media, George Mason University (2021--\textit{present})

Adjunct Professor, Department of History and Art History, George Mason University (2024--\textit{present})

\subsection{Major Affiliations and Fellowships}\label{affiliations-and-fellowships}

Affiliate Fellow, Center for Great Plains Studies, University of Nebraska-Lincoln, Lincoln, NE (2023--\textit{present})

Member, Environmental History Action Collaborative, (2020--\textit{present})

\subsection{Editorial and Advisory Appointments}\label{editorial-and-advisory-appointments}

Advisory Board, Open Online Newspaper Initiative (2022--\textit{present})

Advisory Board, Sourcery (2021--\textit{present})

\subsection{Books \& Selected Digital Projects}\label{books}

\textit{Silicon Valley and the Environmental Inequalities of High-Tech Urbanism}. Norman: University of Oklahoma Press, 2024.

\emph{Machines in the Valley: Growth, Conflict, and Environmental Politics in Silicon Valley}, (2024): \url{https://machinesinthevalley.org}. (primary investigator)

\emph{Connecting Threads}, Roy Rosenzweig Center for History and New Media, (in progress, 2022--): \url{https://connectingthreads.co.uk}. (co-PI)

\emph{American Religious Ecologies}, Roy Rosenzweig Center for History and New Media (in progress, 2021--): \url{https://religiousecologies.org}. (senior developer)

\textit{Digital Community Engagement: Partnering Communities with the Academy}, with Rebecca Wingo and Paul Schadewald. Cincinnati: University of Cincinnati Press, 2020. (Awarded the National Council on Public History Book Award, 2021).

\emph{American Indian Digital History Project}, (in progress, 2017--): \url{https://aidhp.com}. (research director)

\subsection{Selected Peer-Reviewed Journal Articles \& Book Chapters}\label{peer-reviewed}

``Creating Capacity for Research Data Services at Regional Universities: A Case Study,'' co-author with Omer Farooq and Kate Ehrig-Page, in \emph{Teaching Research Data Management}, ed. Julia Bauder. ALA Editions, 2022.

``Hidden Voices: A Case Study Analysis of Subject Headings for Book Titles on Women in Science,'' co-author with Heidi Blackburn, \textit{Science and Technology Libraries}, (2022). \url{https://doi.org/10.1080/0194262X.2022.2040405}.

``Teaching Data Literacy for Civic Engagement: Resources for Data Capture and Organization,'' co-author with Brandon Locke, \textit{KULA: Knowledge Creation, Dissemination, and Preservation Studies}, vol. 2, no. 1 (Fall 2018). <https://doi.org/10.5334/kula.23>

``Green Dreams, Toxic Legacies: Toward a Digital Political Ecology of Silicon Valley,'' \textit{International Journal of Humanities and Arts Computing}, vol. 11, no. 1 (March 2017): 68--85.

\subsection{Selected External Grants \& Fellowships}\label{grants-and-fellowships}

Connecting Threads: Digitally Connecting Collections and Expanding Public Engagement, NEH Digital Humanities Advancement Grant, awarded, \$130,429.

University of Wyoming American Heritage Center's Travel Grant, awarded, \$750.

Toward an Open Monograph Ecosystem (TOME), 2019, awarded, \$15,000.

Library of Congress Teaching with Primary Sources Grant, 2018, awarded, \$19,750.

\subsection{Selected Presentations}\label{presentations}

``Ranching Interests and Anti-Government Politics in the Sagebrush-Era West,`` at the American Society for Environmental History, March 2024, Denver, Colorado.

``Digital Humanities and the Spatial Turn,'' at the 2023 American Historical Association, January 2023, Philadelphia, Pennsylvania.

``History and the Spatial Turn: Pedagogical Approaches,'' round table discussant, at the 136th American Historical Association, January 2023, Philadelphia, Pennsylvania.

``Space, Time, and Visualizing the London Bills of Mortality,'' Southern History Association, November 11, 2022, Baltimore, Maryland.

``Digitizing and Transcribing the 1926 Census of Religious Bodies,'' Society for the Scientific Study of Religion and the Religious Research Association, November 11-13, 2022, Baltimore, Maryland.

\end{document}
