% Curriculum vitae
% Jason A. Heppler | jason@jasonheppler.org | http://jasonheppler.org
% Updated: 2024-07-30

\documentclass[10pt]{article}

%%% Packages
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry}
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
\usepackage[osf,sc]{mathpazo}
\usepackage{inconsolata}
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing
\usepackage{noto}
\usepackage[T1]{fontenc}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

\def\myauthor{Jason Heppler}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{George Mason University}
\def\myjob{Senior Web Developer}
\def\mycourtesy{Adjunct. Prof. of History}
\def\myaddress{Roy Rosenzweig Center for History and New Media}
\def\myemail{jason@jasonheppler.org}
\def\myweb{https://jasonheppler.org}
\def\myphone{+1 605-770-5871}
\def\mytwitter{jaheppler}
\def\mygithub{hepplerj}
\def\mypgp{7194 C159 B68D A2B3}
%\def\myorcid{0000-0003-4158-6186}

\date{} 
\def\mykeywords{Jason, Heppler, Jason Heppler, Vita, CV, Resume}

% HEADINGS
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\sectionfont{\sffamily\bfseries\Large} 
\subsectionfont{\sffamily\bfseries\scshape\normalsize} 
\subsubsectionfont{\sffamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1}
% tightlist fix
\def\tightlist{}

%%%------------------------------------------------------------------------
% PDF SETUP
%%%------------------------------------------------------------------------

\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Jason A. Heppler - CV}, pdfauthor={Jason A. Heppler}]{hyperref}

%%%------------------------------------------------------------------------
%%% Document 
%%%------------------------------------------------------------------------

\begin{document}

\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

%%%------------------------------------------------------------------------
%%% Version date
%%%------------------------------------------------------------------------

%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------

\noindent{\LARGE Jason A. Heppler}\\[-0.1in] \\

\vskip 0.05in

\noindent{\footnotesize \textemdash} \\
\noindent{\normalsize \myaddress} \\
\noindent{\normalsize George Mason University} \\ 
\noindent{\footnotesize \textemdash} \\

\begin{minipage}[t]{2.95in}
  \flushleft {
  \footnotesize
  4400 University Drive, MSN 1E7 \\
  \vspace{-0.05in} Fairfax, \textsc{VA} 22030}
\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{3.5in}
  \flushleft \footnotesize
  \texttt{\href{mailto:\myemail}{\myemail}} \\
  \texttt{\href{\myweb}{\myweb}} \\ 
  \texttt{\href{https://orcid.org/0000-0003-4158-6186}{0000-0003-4158-6186}} \\ 
\end{minipage}

\vskip 0.5in


\section{Professional Experience}

\textbf{George Mason University}, Fairfax, VA

\quad Senior Developer, Roy Rosenzweig Center for History and New Media, 2021--\textit{present}

\quad Adjunct Professor, Department of History and Art History, 2024--\textit{present}

\vspace{.4cm}

\textbf{University of Nebraska at Omaha}, Omaha, NE

\quad Digital Engagement Librarian, UNO Libraries, 2017--2021

\quad Assistant Professor of History (by courtesy), 2017--2021

\quad Subject Specialist, History, UNO Libraries, 2019--2021

\quad Sustainability Faculty, Sustainability Minor Program, 2018--2021

\quad Interim Institutional Repository Coordinator, 2021

\vspace{.4cm}

\textbf{Stanford University}, Stanford, CA

\quad Academic Technology Specialist, Department of History and \href{http://cidr.stanford.edu}{Center for Interdisciplinary Digital Research} (CIDR), 2013--2017

\quad Research staff, \href{http://cesta.stanford.edu}{Center for Spatial and Textual Analysis} (CESTA), 2013--2017

\quad Lecturer, Department of History, 2013--2016

\vspace{.4cm}

\textbf{\href{https://endangereddataweek.org}{Endangered Data Week}}

\quad Co-founder and organizer, 2017--2021

\vspace{0.2cm}

\subsection*{Major Affiliations and Fellowships}

\textbf{Affiliate Fellow}, Center for Great Plains Studies, University of Nebraska-Lincoln, Lincoln, NE (2023--\textit{present})

\textbf{Affiliate Scholar}, Connecting the Interstates, NEH ODH Planning Grant (2020--\textit{present})

\textbf{Member}, Environmental History Action Collaborative Working Group, Environmental Data \& Governance Initiative (2020--\textit{present})

\textbf{Mentor}, Open Leadership Program, Mozilla Foundation (2018--2020)

\subsection*{Editorial and Advisory Appointments}

\textbf{Advisory Board}, Open Online Newspaper Initiative (2022--\textit{present})

\textbf{Advisory Board}, Sourcery (2021--\textit{present})

\textbf{Digital Content Advisory Board}, \href{http://www.americanyawp.com/}{The American Yawp} (2014--\textit{present})

\textbf{Editorial Board}, \textit{Studies in Midwestern History}, Midwestern History Association (2017--2021)

\textbf{Editorial Board}, \href{https://uimiddle.wordpress.com/}{The Middle West Review}, University of Nebraska Press (2014--2021)

% Areas of Research and Teaching

\section*{Areas of Research and Teaching}

North American West and Great Plains $\cdot$ Twentieth-century United States $\cdot$ Digital History $\cdot$ Environmental History $\cdot$ Agricultural History $\cdot$ Data Visualization $\cdot$ Public History $\cdot$ Software Development

% Education

\section*{Education}

\textbf{University of Nebraska-Lincoln}, Ph.D., Department of History, August 2016 \\
\textit{Dissertation}: ``Machines in the Valley: Community, Urban Change, and Environmental Politics in Silicon Valley, 1945--1990'', \url{http://digitalcommons.unl.edu/historydiss/86/}. \\
\textit{Advisors}: Patrick Jones (chair), William G. Thomas, Margaret Jacobs, James Garza, Stephen Ramsay

\textbf{University of Nebraska-Lincoln}, M.A., Department of History, May 2009 \\
\textit{Thesis}: ``Framing Red Power: The Trail of Broken Treaties, the American Indian Movement, and the Politics of Media'', \url{http://digitalcommons.unl.edu/historydiss/21/}. \\
\textit{Advisors}: John Wunder (chair), Douglas Seefeldt, Thomas Gannon

\textbf{South Dakota State University}, B.A., History, May 2007 \\
\textit{Undergraduate Thesis}: ``'We Lit a Fire Across Indian Country': The American Indian Movement and the Intellectual Origins of Red Power.'' \\
\textit{Minor}: Economics

% Research

\section*{Research}

% Books

\subsection*{Books}

\textit{Silicon Valley and the Environmental Inequalities of High-Tech Urbanism}. Environment in Modern North America series. Norman: University of Oklahoma Press, 2024.

\textit{Digital Community Engagement: Partnering Communities with the Academy}, co-edited with Rebecca Wingo and Paul Schadewald, <https://ucincinnatipress.manifoldapp.org/projects/digital-community-engagement>. Cincinnati: University of Cincinnati Press, 2020. \\
\quad $\cdot$ Awarded the National Council on Public History (NCPH) Book Award, 2021

\subsection*{Peer-Reviewed Journal Articles}\label{peer-reviewed}

Heidi Blackburn and Jason A. Heppler, "Hidden Voices: A Case Study Analysis of Subject Headings for Book Titles on Women in Science," \textit{Science and Technology Libraries}, (2022). \url{https://doi.org/10.1080/0194262X.2022.2040405}

Jeanne Reames, Jason A. Heppler, and Cory Starman, "Becoming Macedonian: Name Mapping and Ethnic Identity. The Case of Hjphaistion." \textit{Karanos. Bulletin of Ancient Macedonian Studies} (2020), 3, 11-37.

Heidi Blackburn and Jason A. Heppler, "Who is Writing about Women in STEM in Higher Education? A Citation Analysis of Gendered Authorship," \textit{Frontiers in Psychology} 10 (2020). \url{https://doi.org/10.3389/fpsyg.2019.02979}

Heidi Blackburn and Jason A. Heppler, "Women in STEM in Higher Education: A Citation Analysis of the Current Literature," \textit{Science \& Technology Libraries} (2019). \url{https://doi.org/10.1080/0194262X.2019.1645080}

Brandon Locke and Jason A. Heppler, "Teaching Data Literacy for Civic Engagement: Resources for Data Capture and Organization," \textit{KULA: Knowledge Creation, Dissemination, and Preservation Studies} 2 (1) (Fall 2018). \url{https://doi.org/10.5334/kula.23}

"Green Dreams, Toxic Legacies: Toward a Digital Political Ecology of Silicon Valley," \textit{International Journal of Humanities and Arts Computing} vol. 11, no. 1 (March 2017): 68--85. \url{https://doi.org/10.3366/ijhac.2017.0179}

Gabriel Wolfenstein and Jason A. Heppler, ``Crowdsourcing Public Digital History,'' \textit{The American Historian}, March 2015. \url{http://tah.oah.org/content/crowdsourcing-digital-public-history/}

Alex Galarza, Douglas Seefeldt, and Jason A. Heppler, ``A Call to Redefine Historical Scholarship in the Digital Turn,'' \textit{Journal of Digital Humanities}, December 2012. \url{http://journalofdigitalhumanities.org/1-4/a-call-to-redefine-historical-scholarship-in-the-digital-turn/)}

\subsection{Articles}\label{articles}

``How Silicon Valley provides the blueprint for cleaning up our drinking water,'' \textit{The Washington Post}, April 26, 2019. \url{https://www.washingtonpost.com/outlook/2019/04/26/how-silicon-valley-provides-blueprint-cleaning-up-our-drinking-water/}

``Advocacy, Training, and Awareness Through Endangered Data Week,'' co-author with Brandon Locke, Sarah Melton, and Rachel Mattson, \textit{Parameters}, SSRC, February 26, 2018.

``How Silicon Valley Industry Polluted the Sylvan California Dream,'' \textit{The Conversation}, November 15, 2017. \url{https://theconversation.com/how-silicon-valley-industry-polluted-the-sylvan-california-dream-85810}

\subsection{Book Chapters}

"Creating Capacity for Research Data Services at Regional Universities: A Case Study," co-author with Omer Farooq and Kate Ehrig-Page, in \textit{Teaching Research Data Management}, ed. Julia Bauder. ALA Editions, 2022.

"A National Monument," co-author with Douglas Seefeldt, in \textit{The Companion to Custer and the Little Big Horn}, ed. Brad Lookingbill. Hoboken: Wiley and Sons, 2015.

"The American Indian Movement and South Dakota Politics," in \textit{The Plains Political Tradition}, ed. Jon Lauck, John E. Miller, and Donald Simmons. Pierre, SD: South Dakota State Historical Society Press, 2011, 267--287.

\subsection{Other Academic Publications}

Molly Taylor-Polesky and Jason Heppler, "The 1613 Marriage Journey of Elizabeth Stuart: Reflections on Visualizing European Geopolitics on the Brink of the Thirty Years War," Spatial History Project, Stanford University, June 20, 2018: \url{https://web.stanford.edu/group/spatialhistory/cgi-bin/site/pub.php?id=129}.

Arguing with Digital History working group, "Digital History and Argument," white paper, Roy Rosenzweig Center for History and New Media, George Mason University, November 13, 2017: \url{http://rrchnm.org/argument-white-paper/}.

\subsection{Electronic Books}

\textit{The Rubyist Historian: Ruby Fundamentals for Humanities Scholars}. DOI: 10.5281/zendo.9987.

\subsection{Digital History}

\textbf{Project Director}, \textit{Machines in the Valley: Growth, Conflict, and Environmental Politics in Silicon Valley}, 2015--2017.

\textbf{Project Manager}, \textit{William F. Cody Archive}, Center for Digital Research in the Humanities, University of Nebraska-Lincoln, 2011--2013.

\textbf{Project Director}, \textit{"Self-sustaining and a good citizen": William F. Cody and the Progressive Wild West}, Cody Studies, Buffalo Bill Center of the West, 2012.

\textbf{Software Developer and Scholarly Contributor}, \textit{The Buffalo Bill Project}, Department of History, University of Nebraska-Lincoln, 2011--2013 (retired and superseded by \textit{Cody Studies}).

\textbf{Project Director}, \textit{Buffalo Bill's Wild West and the Progressive Image of American Indians}, digital history, 2010--2011 (retired and superseded by \textit{William F. Cody and the Progressive Wild West}).

\textbf{Graduate Digital Editor}, \textit{The Papers of William F. Cody}, Buffalo Bill Historical Center, 2009--2010.

\textbf{Project Director}, \textit{Framing Red Power: The Trail of Broken Treaties, the American Indian Movement, and the Politics of Media}, digital history, 2008--2009.

\subsection{Collaborative Digital Projects}

\textit{Open Source Shakespeare}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2025--\textit{present}): \url{https://www.opensourceshakespeare.org}. (co-PI and project technical lead)

\textit{Connecting Threads}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2022--\textit{present}): \url{https://connectingthreads.co.uk}. (co-PI)

\textit{Death by Numbers}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2021--\textit{present}): \url{https://deathbynumbers.org}. (senior developer)

\textit{American Religious Ecologies}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2018--\textit{present}): \url{https://religiousecologies.org}. (senior developer)

\textit{Collecting These Times: American Jewish Experiences of the Pandemic}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2020--2022): \url{https://collectingthesetimes.org}. (senior developer)

\textit{American Indian Digital History Project} (2017--\textit{present}): \url{http://aidhp.com}. (research director)

\textit{Nebraska Historical} (2017--2020): \url{https://omahahistorical.org}. (project director)

\textit{Silicon Valley Historical} (2016--2020): \url{http://svhistorical.org}. (project director)

\textit{Chinese Railroad Workers in North America}, Stanford University (2013--2016): \url{https://web.stanford.edu/group/chineserailroad/cgi-bin/website/}. (technical lead)

\subsection*{Contributions to Publications}

\textbf{Author}, \href{http://jasonheppler.org}{JasonHeppler.org}, 2008--\textit{present}.

\textbf{Contributor}, \href{http://blogwest.org/}{BlogWest}, 2013--2020.

\textbf{Contributor}, \href{http://whadigitalfrontiers.com/}{Digital Frontiers: A WHA Digital Workshop}, 2010--\textit{present}.

\textbf{Contributor}, \href{http://chronicle.com/blogs/profhacker/}{ProfHacker}, 2012--2013.

\textbf{Contributor}, \href{https://www.insidehighered.com/blogs/gradhacker}{GradHacker}, 2012.

\textbf{Contributor}, \href{http://digitalhistory.unl.edu/}{Doing Digital History}, 2009--2010.

\subsection{Media}

Co-host, \href{http://overanalyze.fireside.fm}{Overanalyze}, podcast, with Andy Wilson, 2016--2017.

Co-founder, \href{http://fiddly.fm}{FiddlyFM}, 2015--2017.

Co-host, \href{http://www.fiddly.fm/firstdraft/}{The First Draft Podcast}, with Elijah Meeks and Paul Zenke, 2014--2016.

\subsection{Select Academic Software}

``Superfundr: An R data package on U.S. Superfund sites,'' R package (2019--\textit{present}): \url{https://github.com/hepplerj/superfundr/}

\subsection{Reviews}

Digital history review of Erika Bsumek, \textit{ClioVis: Visualizing Connections}, in \textit{The Journal of American History} (2024).

Review of Katie Phillips, "Timeline of Empire," in \textit{Reviews in Digital Humanities} (2022). \url{https://reviewsindh.pubpub.org/pub/timeline-of-empire/release/3}

Review of Kathleen A. Cairns \textit{At Home In the World: California Women and the Postwar Environmental Movement} (University of Nebraska Press), in the \textit{Pacific Historical Review} (2022). \url{https://doi.org/10.1093/whq/whac013}

Review of Trevor Owens, \textit{The Theory and Craft of Digital Preservation} (Johns Hopkins University Press), in \textit{The Public Historian} (May 2020). \url{https://doi-org.leo.lib.unomaha.edu/10.1525/tph.2020.42.2.160}

Review of Walter Nugent, \textit{Color Coded: Party Politics in the American West, 1950-2016} (University of Oklahoma Press), in \textit{South Dakota History} (April 2020).

Review of Pamela Riney-Kehrberg, \textit{The Nature of Childhood: An Environmental History of Growing Up in America since 1865} (University Press of Kansas), in \textit{Middle West Review} (Spring 2019). \url{https://doi.org/10.1353/mwr.2019.0030}

Review of Andrew Busch, \textit{City in a Garden: Environmental Transformations and Racial Justice in Twentieth-Century Austin} (University of North Carolina Press), in \textit{Environmental History} (Fall 2018). \url{https://doi.org/10.1093/envhis/emy067}

Digital history review of \textit{Mapping Inequality: Redlining in New Deal America} and \textit{Renewing Inequality: Family Displacements through Urban Renewal}, in \textit{American Panorama: An Atlas of United States History} (University of Richmond), in \textit{American Quarterly} (Fall 2018). \url{http://doi.org/10.1353/aq.2018.0058}

Digital history review of Jay Taylor, \textit{Follow the Money: A Spatial History of In-Lieu Programs for Western Federal Lands} (Stanford Spatial History Project), in \textit{Western Historical Quarterly} (Fall 2018). \url{https://doi.org/10.1093/whq/why049}

Digital history review of \textit{American Panorama: An Atlas of United States History} (University of Richmond), in \textit{Journal of American History} (March 2017). \url{https://doi.org/10.1093/jahist/jaw624}

Digital history review of \textit{North Dakota: People Living on the Land} (State Historical Society of North Dakota), in \textit{The Public Historian} (May 2017). \url{https://doi.org/10.1525/tph.2017.39.2.104}

Review of Bradley Shreve, \textit{Red Power Rising: The National Indian Youth Council and the Origins of Native Activism} (University of Oklahoma Press), in \textit{South Dakota History} (Spring 2012).

Digital tool review, "Google Earth for Historians," in \textit{The Digital History Project} (Summer 2010).

Review of Joseph Trimbach, \textit{American Indian Mafia: An FBI Agent's True Story about Wounded Knee, Leonard Peltier, and the American Indian Movement} (Outskirts Press), in \textit{South Dakota History} (Spring 2009).

Digital tool review, "TokenX as a Historical Research Tool," with Brent M. Rogers, in \textit{The Digital History Project} (July 2009).

Review of Akim Reinhardt, \textit{Ruling Pine Ridge: Oglala Lakota Politics from the IRA to Wounded Knee}, in \textit{South Dakota History}, (Summer 2008).

Digital history review of William G. Thomas et al., "The Countryside Transformed: The Eastern Shore of Virginia, the Pennsylvania Railroad, and the Creation of the Modern Landscape," in \textit{The Digital History Project} (February 2008).

\subsection{Community Outreach and Engagement}

\textbf{Consultant}, \textit{Making Invisible Histories Visible}, \url{http://invisiblehistory.ops.org}, Omaha, Nebraska (2017--2021).

\textbf{Consultant}, Calgary Stampede, Calgary, Alberta, Canada (2019).

\textbf{Organizer}, \textit{Mozilla Global Sprint 2017}, Omaha, Nebraska (2017).

\textbf{Project Lead}, \textit{Mobile Digitization for Rural Community Archives}, University of Nebraska at Omaha, Omaha, Nebraska (2017-2021).

\textbf{Founder}, \textit{Endangered Data Week}, \url{http://endangereddataweek.org}, Omaha, Nebraska (2017--2020).

\textbf{Consulting scholar}, \textit{Santa Clara Valley National Heritage Area} (2016--2017).

\subsection*{Research In-Progress}\label{in-progress}

\begin{itemize}
\item A new regional history of the Sagebrush Rebellion on the Great Plains
\item A history of farmer's markets spanning the 19th and 20th centuries
\item A biography of Wallace Stegner as told through his students
\end{itemize}

\section{Invited Talks and Presentations}

\textbf{Keynote address}, "Digital History and Communities in an Age of Surveillance," Institute for Digital Research in the Humanities (IDRH), University of Kansas, March 7, 2024.

\textbf{Public Historian Speaker Series}, University of Montana, Missoula, Montana, April 4, 2023.

"Visualizing Data in the Liberal Arts," Colorado State University, April 4, 2019, Fort Collins, Colorado.

Panel, "Shaping the Digital Humanities: UNL Alumni," Digital Humanities Forum, University of Nebraska-Lincoln, April 2018, Lincoln, Nebraska.

\textbf{Keynote address}, "Approaching a New Historical Atlas of Midwestern History with Deep Maps and Digital History" Midwestern History Association, June 2017, Grand Rapids, Michigan.

"'Don't Let Industry Do its Business In Our Water!!!': Urban Space and Environmental Politics in Silicon Valley," Ball State University, April 2017, Muncie, Indiana.

Talkback, \textit{The Man Who Shot Liberty Valance}, Omaha Community Playhouse, February 2017, Omaha, Nebraska.

"Doing Digital History in the Classroom," Missouri Valley History Conference, March 2015, Omaha, Nebraska.

"Humanistic Approaches to Data Visualization," \texttt{d3.digitalhumanities()} Meetup, January 2015, San Francisco, California.

Teaching with Technology, Nebraska Wesleyan University, June 2012, Lincoln, Nebraska.

History Club Graduate School Symposium, South Dakota State University, October 2007, Brookings, South Dakota.

\section{Media Appearances}

\href{https://draftingthepast.com/podcast-episodes/episode-45-jason-heppler-wants-tools-that-fit-his-questions/}{\textit{Drafting the Past}}, June 2024.

\href{https://vimeo.com/947498919}{Greenhouse Environmental Humanities Book Talk}, Greenhouse Center for Environmental Humanities, University of Stavanger, Norway, April 2024.

``Alternative Academic Careers,'' GradHacker Podcast, February 2013.

\section*{Conference Papers, Talks, and Workshops}

\subsection*{Papers Presented}

\begin{itemize}
  \item "Ranching Interests and Anti-Government Politics in the Sagebrush-Era West," American Society for Environmental History, March 2024, Denver, Colorado.
  
  \item "Space, Time, and Visualizing the London Bills of Mortality," Southern History Association, November 11, 2022, Baltimore, Maryland.
  
  \item "Digitizing and Transcribing the 1926 Census of Religious Bodies," Society for the Scientific Study of Religion and the Religious Research Association, November 11-13, 2022, Baltimore, Maryland.
  
  \item "'As the people came, the orchards went': Water, Energy, and Land in Silicon Valley, 1945-1970," Annual Meeting of the Agricultural History Society, August 2022, Stavanger, Norway.
  
  \item "Visualizing Silicon Valley's Urban Spaces," panel on \textit{Visualizing the West: Digital History as Process and Product}, 61st Annual Conference of the Western History Association, October 2021, Portland, Oregon.
  
  \item "Hidden Voices: A Data Analysis of Subject Headings for Books on Women in Science," with Heidi Blackburn, American Women of Science: Recovering History, Defining the Future 2020 Symposium, Smithsonian American Women's History Initiative, October 2020, virtual.
  
  \item "'Don't Let Industry Do its Business in our Water!!!' High-Tech Toxics and Environmental Justice in Silicon Valley," American Society for Environmental History, March 2020, Ottawa, Ontario, Canada. (Cancelled due to the pandemic.)
  
  \item "Using data visualization to analyze topic development by business communication students in a one-shot setting," Brick \& Click: An Academic Library Conference, November 2019, Maryville, Missouri.
  
  \item "A citation analysis of journals publishing research on women in STEM in higher education," American Library Association Annual Conference, June 2019, Washington, D.C.
  
  \item "Creating a Culture of Data Consciousness with Endangered Data Week," Mozilla Festival, October 2018, London, United Kingdom.
  
  \item "'Piecemeal, Patchwork, Prop-Up': Urban Planning and Environmental Change in Postwar Silicon Valley," at "You Are Here": An Interdisciplinary Conference on Place, Space, and Embodiment, Creighton University, March 2018, Omaha, Nebraska.
  
  \item "The Tap Water Rebellion: Pollution, High-Tech Industrialization, and Suburban Politics in Silicon Valley," at the American Society for Environmental History, March 2018, Riverside, California (did not attend).
  
  \item "\textit{Oskate Wicasa}, Progressive Thought, and the Digital Publics of Buffalo Bill's Wild West," 57th Annual Western Historical Association, November 2017, San Diego, California.
  
  \item "Introducing the American Indian Digital History Project," at the 57th Annual Western Historical Association, November 2017, San Diego, California.
  
  \item "Mobile Rural Archives Lab," LYRASIS Member Summit, October 2017, Philadelphia, Pennsylvania.
  
  \item "Mapping Silicon Valley" Digital Humanities 2017, August 2017, Montreal, Quebec, Canada.
  
  \item "Digital History, Publics, and Community Engagement," \textit{Information Exchange}, March 2017, Omaha, Nebraska.
  
  \item "Green Dreams, Toxic Legacies: Digital History and the Landscapes of Silicon Valley," Annual Meeting of the American Society for Environmental History, March 2016, Seattle, Washington (did not attend).
  
  \item "From the Laptop to the Archive: Managing Research Data in the Humanities," October 2015, Digital Library Federation Forum, October 2015, Vancouver, British Columbia, Canada.
  
  \item "Mapping Silicon Valley's Environment: Deep Maps and Urban Environmental History" 55th Annual Conference of the Western History Association, October 2015, Portland, Oregon.
  
  \item "Minimal Computing in Digital Humanities," Academic Technology Expo, Stanford University, October 2015.
  
  \item "Networks in the Humanities," lighting talk, with Brian Sarnacki, Rebecca Wingo, and Andy Wilson, HASTAC, May 2015.
  
  \item "Mapping the American West through the U.S. Post," Social Science History Association Annual Meeting, November 2014, Toronto, Canada.
  
  \item "Digital Humanities in the Classroom," Academic Technology Expo, Stanford University, October 2014, Stanford, California.
  
  \item "Spatial History and the Western Past," Six Shooters Lighting Talk, 53rd Annual Conference of the Western History Association, October 2013, Tucson, Arizona.
  
  \item "Programming in the Humanities," proposed and led session, THATCamp American Historical Association, January 2012, Chicago, Illinois.
  
  \item "The American Indian Movement and South Dakota Politics," George McGovern Conference, November 2011, George McGovern Center for Leadership and Public Service, Mitchell, South Dakota.
  
  \item "'This Great and Sovereign Right': Eminent Domain, the Cherokee Nation, and Railroad Law, 1880--1890," 50th Annual Conference of the Western History Association, October 2010, Incline Village, Nevada.
  
  \item "William F. Cody and the Digital Frontier," International Cody Studies Conference, August 2010, Cody, Wyoming.
  
  \item "Framing Red Power: Newspapers and Native Activists during the Trail of Broken Treaties," Digital Humanities Summit, March 2010, Lawrence, Kansas.
  
  \item "'Another Wounded Knee Was Feared': Visualizing Newspaper Narratives of the Trail of Broken Treaties Caravan and American Indian Activism with Digital Tools," 53rd Annual Missouri Valley History Conference, March 2010, Omaha, Nebraska.
  
  \item "Red Power and the Intellectual Origins of the American Indian Movement," 50th Annual Missouri Valley History Conference, March 2007, Omaha, Nebraska.
  
  \item "Tangled Memories: Wounded Knee and the Problem of Memory," 41st Annual Northern Great Plains History Conference, October 2006, Sioux Falls, South Dakota.
  
  \item "Tangled Memories: Wounded Knee and the Problem of Memory," 38th Annual Dakota History Conference, Sioux Falls, South Dakota.
  
  \item "Case Study of the Makah Tribe's Defense of Whaling Rights," 14th Annual SDSU American Indian History and Culture Conference, Brookings, South Dakota.
\end{itemize}

\subsection*{Chair/Comment}

\begin{itemize}
  \item Chair, "Digital History Lightning Talks," Annual Conference of the Western History Association, October 2017, November 2018, October 2019.
  
  \item Chair and comment, "The Digital Second Crusade," The Second Crusade: Chronicles and Perspectives Undergraduate Student Conference, University of Nebraska at Omaha, April 2017, Omaha, Nebraska.
  
  \item Panel Comment, "Integrating Digital History into Research \& Teaching: The American Experience in World War II," Missouri Valley History Conference, March 2017, Omaha, Nebraska.
  
  \item Panel chair, "Sources as Data: Opportunities and Challenges," 131st Annual Meeting of the American Historical Association, January 2017, Denver, Colorado.
  
  \item Panel chair, "Western Encounters, Alliances, and Experiences: Mormons, Indians, and U.S. Federal Law," 54th Annual Conference of the Western History Association, October 2014, Newport Beach, California.
  
  \item Discussion facilitator, "Breakout Session: Games and Learning," Academic Technology Expo, Stanford University, October 2014, Stanford, California.
  
  \item Panel chair, "Exploring Historic Landscapes with Mobile Technology," 53rd Annual Conference of the Western History Association, October 2013, Tucson, Arizona.
  
  \item Panel chair, Fourth Annual James A. Rawley Conference in the Humanities, University of Nebraska-Lincoln, April 2009.
  
  \item Panel chair, Third Annual James A. Rawley Conference in the Humanities, University of Nebraska-Lincoln, April 2008.
\end{itemize}

\subsection*{Roundtables}

\begin{itemize}
  \item "History and the Spatial Turn: Pedagogical Approaches," round table discussant, at the 136th American Historical Association, January 2023, Philadelphia, Pennsylvania.
  
  \item "Uncovering the Work of Women in Science in Library, Archive, and Museum Collections," American Women of Science: Recovering History, Defining the Future 2020 Symposium, Smithsonian American Women's History Initiative, October 2020, virtual.
  
  \item "Housing, Belonging, and Displacement in the 20th-Century West," 60th Annual Conference of the Western History Association, October 2020, virtual.
  
  \item "It's a Gamble: Luck, Chance, and Failure as a Historian," round table discussant, 59th Annual Conference of the Western History Association, October 2019, Las Vegas, Nevada.
  
  \item "Passages from Quantitative History to Digital Humanities," round table discussant, at the 133rd American Historical Association, January 2019, Chicago, Illinois.
  
  \item "Arguing with Digital History," roundtable discussant, at the 132nd American Historical Association, January 2018, Washington, D.C.
  
  \item "Digital History Roundtable," roundtable discussant, 150th Annual Meeting of the American Historical Association, January 2016, Atlanta, Georgia (did not attend).
  
  \item "The Graduation Threshold: A Discussion on Bridging the Gap from Graduation to Employment," co-organizer and roundtable discussant with Elaine Nelson, Leisl Carr-Childers, Sarah Keyes, and Elise Boxer, 55th Annual Conference of the Western History Association, October 2015, Portland, Oregon.
  
  \item "Digital Scholarship, Academic Careers, and Tenure," roundtable with Jana Remy, Andrew Torget, Mills Kelly, and Katina Rogers, 129th Annual Meeting of the American Historical Association, January 2015, New York City, New York.
  
  \item "Digital Pedagogy for History: Lightning Round," roundtable, 129th Annual Meeting of the American Historical Association, January 2015, New York City, New York.
  
  \item "The Digital History Seminar," round table, with Douglas Seefeldt, Brent Rogers, and Michelle Tiedje, 126th Annual Meeting of the American Historical Association, January 2012, Chicago, Illinois.
  
  \item "Historical Scholarship in the Digital Age: Asking New Questions with Digital Technologies," roundtable discussion, 51st Annual Conference of the Western Social Sciences Association, April 2009, Albuquerque, New Mexico.
  
  \item "Sandoz's Environment: \textit{Old Jules} and 'The Vine'," roundtable, 5th Annual Mari Sandoz Heritage Society Conference, March 2008, Chadron, Nebraska.
\end{itemize}

\subsection*{Working Groups/Workshops}

\begin{itemize}
  \item "Data Visualization for History," Institute for Digital Research in the Humanities (IDRH), University of Kansas, March 7, 2024.
  
  \item Attendee, IIIF 2023 Annual Conference, June 2023, Naples, Italy.
  
  \item "The Basics of Static Sites," Roy Rosenzweig Center for History and New Media, George Mason University, November 2022, Fairfax, Virginia.
  
  \item "Mapping Urban Planning and Environmental History in Silicon Valley," Spatial History Working Group, Center for History and New Media, George Mason University, November 2021, Fairfax, Virginia.
  
  \item Attendee, National Council on Public History Annual Meeting, March 2021, virtual.
  
  \item Attendee, \textit{Data Practices Conference}, Stanford University, October 2020, Stanford, California (virtual).
  
  \item Attendee, \textit{Practicing Pedagogies Summer Teaching Summit}, University of Nebraska-Lincoln, May 2020, Lincoln, Nebraska (virtual).
  
  \item Attendee, Nebraska Library Association's College \& University Section and Technical Services Round Table, May 2020, virtual.
  
  \item Attendee, CSV Conf, May 2020, virtual.
  
  \item Attendee, Innovation in Pedagogy and Technology Symposium, May 2020, Lincoln, Nebraska (virtual).
  
  \item Attendee, \textit{Railroads in Native America: Reflections on the 150th Anniversary of the Transcontinental Construction}, University of Nebraska at Omaha, September 2019, Omaha, Nebraska.
  
  \item Attendee, \textit{Practicing Pedagogies Summer Teaching Summit}, University of Nebraska-Lincoln, May 2019, Lincoln, Nebraska.
  
  \item Attendee, Innovation in Pedagogy and Technology Symposium, May 2019, Lincoln, Nebraska.
  
  \item \textit{Dynamic Digital Methods for Integrating Local History into Public History Institutions and the K-16 Classroom}, one-day workshop given at the 58th Annual Western Historical Association, sponsored by the WHA Committee on Teaching and Public Education, St. Mary's University, October 2018, San Antonio, Texas.
  
  \item Attendee, \textit{Practicing Pedagogies Summer Teaching Summit}, University of Nebraska-Lincoln, May 2018, Lincoln, Nebraska.
  
  \item Co-convenor, \textit{Digital Community Engagement Symposium}, Macalester College, May 2018, St. Paul, Minnesota.
  
  \item \textit{Networks and Network Visualization}, one-day workshop given at the 132nd American Historical Association, January 2018, Washington, D.C.
  
  \item "Arguing with Digital History," invited attendee for two-day workshop, Roy Rosenzweig Center for History and New Media, George Mason University, September 2017, Arlington, Virginia.
  
  \item Attendee, Innovation in Pedagogy and Technology Symposium, May 2017, Lincoln, Nebraska.
  
  \item \textit{Mapping and Network Analysis Workshop}, Digital Scholarship Lab, Ball State University, April 12, 2017, Muncie, Indiana.
  
  \item Attendee, Midwest Archives Conference, April 2017, Omaha, Nebraska.
  
  \item Attendee, Digital Humanities Forum, University of Nebraska-Lincoln, April 2017, Lincoln, Nebraska.
  
  \item \textit{Digital Drop-In Sessions}, participant, 131st American Historical Association, January 2017, Denver, Colorado.
  
  \item Attendee, \textit{Flat Places, Deep Identities: Mapping Nebraska and the Great Plains}, Great Plains Symposium, March 2017, Lincoln, Nebraska.
  
  \item \textit{Networks and Network Visualization}, one-day workshop given at the 131st American Historical Association, January 2017, Denver, Colorado.
  
  \item \textit{Research Tools for your Thesis}, one-day workshop taught at Stanford University for the Bing Honors College Program, September 2016, Stanford, California.
  
  \item \textit{Digital Humanities Workshop}, two-day workshop taught at Colorado State University for the Carl A. Bimson Humanities Seminar, July 26--27, 2016, Fort Collins, Colorado.
  
  \item "Getting Started with Omeka," \textit{Digital Humanities Skills Workshop}, Center for Spatial and Textual Analysis, Stanford University, January 2016, Stanford, California.
  
  \item \textit{Data Preparation and Data Uncertainty}, one-day workshop given at the 130th Annual Meeting of the American Historical Association, January 2016, Atlanta, Georgia (did not attend).
  
  \item Working group facilitator, "Public History as Digital History as Public History," National Council on Public History Annual Meeting, Nashville, Tennessee, April 2015.
  
  \item Attendee, mediaX Games and Learning Conference, Stanford University, May 2014, Stanford, California.
  
  \item \textit{Digital History Workshop}, Space, Materials, and Media Conference, Stanford University, September 2013.
  
  \item \textit{Introduction to GIS}, session co-leader with Katie McDonough, THATCamp Alt-Ac, University of California-Berkeley, Berkeley, California, October 2013.
  
  \item \textit{Introduction to Gephi}, workshop co-leader with Ryan Cordell, Digital Humanities Summer Institute, Victoria, British Columbia, June 2013.
  
  \item Attendee, THATCamp American Historical Association, January 2012, Chicago, Illinois.
  
  \item "Improving Writing in the Survey Course," with William G. Thomas and Leslie Working, Teaching History Forum, Department of History, University of Nebraska-Lincoln, October 2009.
\end{itemize}

\subsection*{Posters}

\begin{itemize}
  \item "American Religious Ecologies," with Caroline Greer, Lincoln Mullen, and John Turner, at the 136th American Historical Association, January 2023, Philadelphia, Pennsylvania.
  
  \item "Hidden Voices: A Data Analysis of Subject Headings for Books on Women in STEM," with Heidi Blackburn, Association of College \& Research Libraries Annual (ACRL) Meeting 2021, April 2021, virtual.
  
  \item "Using Maps and Metadata to Teach the History of Silicon Valley," Third Annual Academic Technology Expo, Stanford University, October 2016, Stanford, California.
  
  \item Electronic poster session, "Mapping Silicon Valley's Environmentalism," 130th Annual Meeting of the American Historical Association, January 2016, Atlanta, Georgia. (did not attend)
  
  \item "The William F. Cody Archive," electronic poster session, Center for Great Plains Studies Symposium, March 2012, Lincoln, Nebraska.
\end{itemize}

\section{Grants and Fellowships}

\subsection*{External (\$43,400)}

\begin{itemize}
  \item Open Source Shakespeare, in review, (Co-Principal Investigator and Project Technical Lead)
  \item University of Wyoming American Heritage Center's Travel Grant, awarded, \$750.
  \item Public Engagement with Historical Records, National Historical Publications \& Records Commission, National Archives, not awarded.
  \item Toward an Open Monograph Ecosystem (TOME), 2019, awarded, \$15,000.
  \item Humanities Nebraska Grant, American Indian Digital History Project, 2019, not awarded.
  \item Library of Congress Teaching with Primary Sources Grant, 2018, awarded, \$19,750.
  \item "Mobile Archives for Rural Communities," LYRASIS Catalyst Fund, University of Nebraska at Omaha, 2017, awarded, \$5,500.
  \item Digital Humanities Summer Institute Tuition Scholarship, University of Victoria, British Columbia, Canada, 2014, awarded, \$800.
  \item Digital Humanities Summer Institute Tuition Scholarship, University of Victoria, British Columbia, Canada, 2013, awarded, \$800.
  \item Nebraska Humanities Council Mini Grant, James A. Rawley Conference, University of Nebraska-Lincoln, 2010, awarded, \$800.
\end{itemize}

\subsection*{Internal (\$9,105)}

\begin{itemize}
  \item Civic Participation Grant, University of Nebraska at Omaha, 2020, \$1,000.
  \item Eugene and Sunny Thomas Fund, University of Nebraska at Omaha Libraries, University of Nebraska at Omaha, 2018, \$5,500.
  \item Faculty Research Grant, Charles W. \& Mary Caldwell Martin Fund, University of Nebraska at Omaha, 2017, \$725.
  \item Office of International Affairs Seed Grant, Stanford University, 2014, not awarded.
  \item John F. Stover Fellowship, Department of History, University of Nebraska-Lincoln, 2012, awarded, \$400.
  \item Plains Humanities Alliance Grant, James A. Rawley Conference, University of Nebraska-Lincoln, 2010, awarded, \$500.
  \item Sheldon Travel Fund Award, Department of History, University of Nebraska-Lincoln, 2010, awarded, \$600.
  \item Sheldon Fund Award, Department of History, University of Nebraska-Lincoln, 2010, awarded, \$380.
  \item Addison E. Sheldon Fellowship, Department of History, University of Nebraska-Lincoln, 2009, funded.
  \item August Edgren Fellowship, College of Arts and Sciences, University of Nebraska-Lincoln, 2007, funded.
\end{itemize}

\section{Awards and Honors}

\begin{itemize}
  \item External Funding Award Recipient and First Time Award, First Annual Faculty Research Awards, Office of Research and Creative Activity, University of Nebraska at Omaha, February 2018.
  \item University Libraries Influence Award, University of Nebraska-Lincoln Libraries, 2011.
  \item Dov Ospovat Memorial Award for Distinguished Graduate Research Paper, University of Nebraska-Lincoln, 2009.
  \item Schultz-Werth Award for Outstanding Undergraduate Research Paper, South Dakota State University, 2007.
  \item Phi Alpha Theta Honor Society, South Dakota State University, 2005--2007.
\end{itemize}

\section{Professional Development}

\subsection*{Conferences and Workshops}
\begin{itemize}
  \item RRCHNM--C\textsuperscript{2}DH Education in Digital History Summit, Roy Rosenzweig Center for History and New Media and the Luxembourg Centre for Contemporary and Digital History, April 6, 2022.
  
  \item Attendee, "Meville Nelles Hoffman Lecture in Environmental History," York University, January 13, 2022.
  
  \item RRCHNM--C\textsuperscript{2}DH Education in Digital History Summit, Roy Rosenzweig Center for History and New Media and the Luxembourg Centre for Contemporary and Digital History, December 9 \& 16, 2021.
  
  \item "Equity in Action: Fostering an Antiracist Library Culture," Library Journal, February 23-March 9, 2021.
  
  \item "Digital Humanities and Spatial History: Atlantic World Stories," by Zephyr Frank, UCL Centre for Digital Humanities, February 23, 2021.
  
  \item "The Power of Allies for an Inclusive Culture," American Management Association, February 18, 2021.
  
  \item Introduction to Norwegian II, University of Oslo (UiO), via Future Learn. Completed 2020.
  
  \item Indigenous Canada, University of Alberta. Completed 2020.
  
  \item Elements of AI, University of Helsinki. Completed 2020.
  
  \item "How do we respond to anti-Black racism in urbanist practices and conversations?," Canadian Urban Institute, June 10, 2020.
  
  \item Keep Teaching Summer Series, Office of Digital Learning, University of Nebraska at Omaha, weekly webinar series, June 24--August 4, 2020.
  
  \item COVID-19 Contact Tracing, Johns Hopkins University, via Coursera. Completed 2020.
  
  \item Python for Data Science, University of California-San Diego, via edX. Completed 2020.
  
  \item Research Data Management and Sharing, The University of North Carolina at Chapel Hill, via Coursera. Completed 2020.
  
  \item Norwegian for Beginners I, Norwegian University of Science and Technology (NTNU), via Future Learn. Completed 2020.
  
  \item Introduction to Norwegian I, University of Oslo (UiO), via Future Learn. Completed 2020.
  
  \item "Text Mining with HathiTrust: An Introduction for Librarians," May 4, 2020.
  
  \item Red Hat Summit, sessions on AI, data, code, diversity and inclusion, and analytics, virtual event, April 28-29, 2020.
  
  \item "Solve Climate by 2030," Nebraska Power Dialog, April 12, 2020.
  
  \item "Going Remote Q\&A Livestreams," Basecamp, March 24-April 2, 2020.
  
  \item "Fighting the Climate Crisis," National Resource Defense Council, teleconference, December 17, 2019.
\end{itemize}

\subsection*{Training and Workshops}
\begin{itemize}
  \item Service Learning Seminar, Service Learning Academy, University of Nebraska at Omaha, July 2018.
  
  \item Mozilla Open Leadership Framework Coaching, Mozilla Foundation, February--June 2018.
  
  \item Mozilla Open Leaders Training: Mentorship and Training on Working Open, Mozilla Foundation, February--June 2018.
  
  \item "Starting a Discussion (Leading to Action)," Humanities Symposium, University of Nebraska at Omaha, February 2018.
  
  \item Python for Data Science and Machine Learning Bootcamp, taught by Jose Portilla, via Udemy. Completed 2017.
  
  \item Data Science and Machine Learning Bootcamp with R, taught by Jose Portilla, via Udemy. Completed 2017.
  
  \item The Data Scientist's Toolbox, John Hopkins University, via Coursera. Completed 2017.
  
  \item Statistical Thinking for Data Science and Analytics, Columbia University Data Science Institute, via EdX. Completed 2017.
\end{itemize}

\subsection*{Symposiums and Workshops}
\begin{itemize}
  \item Historical Trauma: Conquest, Genocide, and John Wayne, and WE are still here, Carolyn Fiscus, Tribal Court Improvement Program, Omaha, Nebraska, September 2017.
  
  \item Collections as Data: IMPACT, Library of Congress, July 2017.
  
  \item Open Leadership 101, Mozilla Foundation, 2017.
  
  \item Pre-Tenure Faculty Leadership Forum, University of Nebraska at Omaha, 2017--2021.
  
  \item Computation + Journalism Symposium, Stanford University, September 2016.
  
  \item UseR! Conference, Stanford University, June 2016.
  
  \item Workshop, "CartoDB@Stanford," Stanford University, March 2015.
  
  \item Participant, "Desktop Fabrication and Physical Computing," Digital Humanities Summer Institute, University of Victoria, British Columbia, Canada, June 2014.
  
  \item Workshop, "Networks in History," Center for Spatial and Textual Analysis, Stanford University, May 2014.
  
  \item Workshop, "See, Think, Design, Produce," Jonathan Corum, Bret Victor, Mike Bostock, and Edward Tufte, San Jose, California, May 2014.
  
  \item Symposium, Hestia2, Stanford University, November 2013.
  
  \item Workshop, "Geo for Higher Education Summit," Google, Mountain View, California, July 2013.
  
  \item Participant, "Geographic Information Systems," Digital Humanities Summer Institute, University of Victoria, British Columbia, Canada, June 2013.
  
  \item Symposium, "Visualization and the Research Process," Center for Spatial and Textual Analysis, Stanford University, May 2013.
  
  \item Workshop, Edward Tufte Visualization Workshop, San Jose, California, May 2013.
  
  \item Workshop, "Visualizing Complexity and Uncertainty," Stanford Humanities Center, Stanford University, 2013.
  
  \item Workshop, "Cutting Edge Geospatial Technologies with Google Tools," Stanford University, February 2013.
  
  \item Workshop, "Digital Frontiers: A Digital History Workshop," Western History Association, Denver, Colorado, October 2012.
  
  \item Workshop, "Open Access," Graduate Student Association, University of Nebraska-Lincoln, October 2011.
  
  \item Workshop, "Building Your C.V. and Utilizing Social Networking for Your Academic Career," HGSA Workshop, September 2011.
  
  \item Participant, Cody Camp, Cody, Wyoming, July 2011.
  
  \item Session attendee, "Project Management," University of Nebraska-Lincoln Libraries, March 2011.
  
  \item Workshop, "Digital Frontiers: A Digital History Workshop," Western History Association, Incline Village, Nevada, October 2010.
  
  \item Workshop, Nebraska Digital Workshop, Center for Digital Research in the Humanities, University of Nebraska-Lincoln, 2008, 2009, 2010, 2011.
  
  \item Workshop, "Mapmaking in the Humanities," remote participation, Electronic Data Center, Emory University, May 2009.
  
  \item Workshop, "Introduction to XML," Brian Pytlik-Zillig, Center for Digital Research in the Humanities, University of Nebraska-Lincoln, October 2007.
\end{itemize}

\section{Teaching}

\subsection*{NEH Institute for Advanced Topics in the Digital Humanities}

\begin{itemize}
  \item Digital Methods for Military History (June 2021), George Mason University
\end{itemize}

\subsection*{Digital Humanities Summer Institute}

\begin{itemize}
  \item R, Interactive Graphics, and Data Visualization for the Humanities, with Lincoln Mullen (June 2016), University of Victoria.
\end{itemize}

\subsection*{George Mason University (2021--\textit{present})}

\begin{itemize}
  \item HIST 694: Digital Public History (Spring 2024)
  \item SpaceCamp, spatial history workshop (Spring 2022)
  \item Various workshops with the Data \& Spatial History Working Group, 2021--\textit{present}
\end{itemize}

\subsection*{University of Nebraska at Omaha (2017-2021)}

\subsubsection*{Courses}

\begin{itemize}
  \item HIST 4900: Introduction to Digital Humanities independent study (Spring 2018) (3 credits)
\end{itemize}

\subsubsection*{Library Instruction}

\begin{itemize}
  \item BootcampR: An Introduction to R (Spring 2020)
  \item Guest lecture for ISQA 4000/8086: From Data to Decisions (Fall 2019)
  \item Guest lecture for HIST 4990: Senior Research Seminar (Spring 2019)
  \item Guest lecture for HIST 4740: Comparative Genocide (Spring 2019)
  \item Guest lecture for HIST 1000: World Civilizations (Fall 2018)
  \item Guest lecture for HIST 4910: Vietnam War (Fall 2018)
  \item Guest lecture for HIST 4400: Native American History (Fall 2018)
  \item Guest lecture for HIST 2980: Historical Methodology (Fall 2017, Spring 2018, Fall 2018, Spring 2019, Fall 2019, Spring 2020, Fall 2020, Spring 2021)
  \item Guest lecture for ENGL 3000: Louise Erdrich (Spring 2018)
  \item Guest lecture for PA 3000: Applied Statistics and Data Management (Fall 2017)
  \item Guest lecture for HIST 9100: Ancient Macedonia (Spring 2017)
\end{itemize}

\subsection*{Stanford University (2013--2016)}

\begin{itemize}
  \item Digital History Reading Group (2015--2016)
  \item Digital History: Sources, Methods, Problems (\href{http://jasonheppler.org/teaching/hist205f.2014/}{Fall 2014}) (5 credits)
  \item \textit{Doing Digital History} workshop curriculum, Department of History (Winter 2013 and Fall 2013)
\end{itemize}

\subsection*{University of Nebraska-Lincoln (2008--2010)}

\begin{itemize}
  \item Teaching assistant, HIST 201: U.S. before 1877 (Prof. Brenden Rensink, Fall 2010)
  \item Teaching assistant, HIST 202: U.S. since 1877 (Prof. William G. Thomas, Spring 2009)
  \item Teaching assistant, HIST 150: African Culture and Civilization (Prof. Dawne Curry, Fall 2008)
\end{itemize}

\subsection*{Guest Lectures}

\begin{itemize}
  \item "Career Pathways for Historians," guest lecture, Digital Public History, Prof. Claire DuLaney and Prof. Lori Schwartz, University of Nebraska at Omaha, Fall 2023.
  \item "Getting Started with Digital History," guest lecture, HIST 688: History and Material Culture in the Digital Age, George Mason University, Prof. Deepthi Murali, Fall 2023.
  \item "Mapping Silicon Valley's Environment," guest lecture, HIST 696: Clio Wired, George Mason University, Prof. Lincoln Mullen, Fall 2022.
  \item "Introduction to Data Visualization," guest lecture, University of Nebraska at Omaha, Lect. B. Shine Cho, Spring 2017.
  \item "Digital Dissertations," discussion leader, Digital Humanities Fellows, Center for Spatial and Textual Analysis, Stanford University, Spring 2016.
  \item "Spatial History," guest lecture, Stanford University, COMPLIST 238/ENGLISH 229D/HISTORY 229D: Introduction to Digital Humanities, Lect. Brian Johnsrud and Mike Widner, Winter 2014.
  \item "Mass Media and the American Indian Movement," guest lecture, University of Nebraska-Lincoln, COMM 189H: Communications and Social Movements, Prof. Carly Woods, Fall 2011.
  \item "Thomas Jefferson and the American West," guest lecture, University of Nebraska-Lincoln, HIST 201: U.S. History before 1877, Prof. Brenden Rensink, Fall 2010.
  \item "Empire of Liberty: Culture, Society, and Politics in the Early Republic," guest lecture, University of Nebraska-Lincoln, HIST 201: U.S. History before 1877, Prof. Brenden Rensink, Fall 2010.
  \item "Show Indians and Buffalo Bill's Wild West," guest lecture, University of Nebraska-Lincoln, HIST 359: Mythic West, Prof. Douglas Seefeldt, Spring 2010.
  \item "The Origins of Red Power and the American Indian Movement," guest lecture, University of Nebraska-Lincoln, HIST 202: U.S. History after 1877, Prof. William G. Thomas, Spring 2009.
\end{itemize}

\subsection*{Workshops}

\begin{itemize}
  \item "TextExpander," with Paul Zenke, Stanford Mobile Users Group, Stanford University, October 2014, Stanford, California.
  \item "1Password," with Vijoy Abraham and Paul Zenke, Stanford Mobile Users Group, Stanford University, May 2014, Stanford, California.
  \item "Research Management with Digital Tools," guest speaker, Prof. Gordon Chang, Stanford University, HIST 460: America in the World, February 2014.
  \item "Using Technology in Teaching," discussion participant, Prof. Nancy Kollman, Stanford University, HIST 305: Workshop in Teaching History, May 2013.
  \item "Frameworks for Thinking about Teaching with Technology," discussion participant, Stanford University, Center for Teaching and Learning, May 2013.
  \item "Online Learning and History Education," discussion participant, Stanford University, Center for Teaching and Learning, May 2013.
  \item "Digital Frontiers: A Digital History Workshop," workshop co-leader, Western History Association, Denver, Colorado, October 2012.
  \item "Building Your C.V. and Utilizing Social Networking for Your Academic Career," workshop co-leader, History Graduate Student Association Workshop, September 2011.
  \item "Introduction to XML/XSLT," workshop leader, University of Nebraska-Lincoln, HIST 970: Digital History Seminar, Spring 2011.
\end{itemize}

\subsection*{Discussion Leader}

\begin{itemize}
  \item Discussion leader, "The Dust Bowl," Prof. Douglas Seefeldt, HIST 352: American West since 1900, Spring 2012.
  \item Discussion leader, "Buffalo Bill's Wild West," Prof. Douglas Seefeldt, HIST 352: American West since 1900, Spring 2011.
  \item Discussion leader, Upton Sinclair's \textit{The Jungle}, Prof. William G. Thomas, HIST 202: U.S. After 1877, Spring 2009.
\end{itemize}

\subsection*{Professional Development}

\begin{itemize}
  \item Workshop, Graduate Teaching Assistant Workshop, Department of History, University of Nebraska-Lincoln, August 2010.
\end{itemize}

\subsection*{Advising}

\subsubsection*{Graduate Students}

\begin{itemize}
  \item Rebecca Wall, African Colonial Employees Project, Stanford University, 2014--2015
  \item Liz Jacob, African Colonial Employees Project, Stanford University, 2014--2015
\end{itemize}

\subsubsection*{Graduate Interns}

\begin{itemize}
  \item J.P. Obley, William F. Cody Archive, University of Nebraska-Lincoln, 2012
  \item Andrew Tully, William F. Cody Archive, University of Nebraska-Lincoln, 2012
\end{itemize}

\subsubsection*{Undergraduate Advising}

\begin{itemize}
  \item Julia Laurence, Crowdsourcing Railroads, Stanford University, 2015
  \item Rahul Singireddy, Chinese Input, Stanford University, 2015
  \item KJ Fryauff, Follow the Money Project, Stanford University, 2015
  \item KJ Fryauff, Chinese Railroad Workers Project, Stanford University, 2014
  \item Jocelyn Hickcox, Geography of the Post, Stanford University, 2013
  \item Tara Balakrishnan, Geography of the Post, Stanford University, 2013
  \item Jared Roehrich, William F. Cody Archive, University of Nebraska-Lincoln, 2011--2012
\end{itemize}

\subsubsection*{Student Supervision \& Management}

\begin{itemize}
  \item Alex Ramsey, American Indian Digital History Project, UNO, 2020
  \item Aaron Burbach, American Indian Digital History Project, UNO, 2020
  \item Haji Salad, Mobile Community Archives, UNO, 2019-2020
  \item Sara Ibrahim, Mobile Community Archives, UNO, 2019
  \item Isis Hernandez-Troche, Mobile Community Archives, UNO, 2018-2019
  \item Cory Starman, Haphastian Place Naming, UNO, 2018-2019
\end{itemize}

\subsection*{Directed Readings, Independent Studies, and Creative Projects}

\begin{itemize}
  \item Readings in Digital History, University of Nebraska at Omaha, Cory Starman, Spring 2018.
  \item Readings in Digital History, University of Nebraska at Omaha, Christine Taylor, Spring 2018.
\end{itemize}

\section{Computing Platforms and Digital Humanities}

\subsection*{Data analysis}
Python, R (programming language), D3.js (visualization), QGIS / ArcGIS (mapping)

\subsection*{Programming languages}
Go, R, Javascript, Python, Ruby, PHP, Unix shell scripts

\subsection*{Data science}
pandas, tidyverse, ggplot, Plotly

\subsection*{Versioning}
Git, GitHub, GitLab, SVN

\subsection*{Web Frameworks/Content Management Systems}
Django, Vue, Hugo, Omeka \& Omeka S

\subsection*{Operating Systems}
Linux, macOS/iOS, Windows

\subsection*{Database Systems/Persistence}
PostgreSQL, SQLite, MySQL

\subsection*{Web/Markup Languages}
HTML, CSS, JSON, XML, \LaTeX

\subsection*{Systems Administration}
Linux, Apache

\subsection*{Applications}
Apple Office Suite, Microsoft Office, Adobe Photoshop, Final Cut Pro

\section{Languages}
English (native proficiency), Norwegian (bokml) (beginner proficiency)

\section{Professional Organizations and Service}

\subsection*{Membership in Professional Organizations}

\begin{itemize}
  \item American Historical Association
  \item Western History Association
  \item Southern History Association
  \item Organization of American Historians
  \item National Council on Public History
  \item American Society for Environmental History
  \item Agricultural History Society
\end{itemize}

\subsection*{Offices in Professional Organizations}

\subsubsection*{Western History Association}

\begin{itemize}
  \item Program Committee, 2018 Annual Meeting, San Antonio, Texas, 2017-2018.
  \item Digital Scholarship Committee, 2011--\textit{present} (Committee chair, 2017--2020)
\end{itemize}

\subsubsection*{Alliance of Digital Humanities Organizations}

\begin{itemize}
  \item DHTech Special Interest Group, 2021--\textit{present}
  \item Program reviewer, Digital Humanities Conference 2020, ADHO Conference Coordinating Committee, Ottawa, Canada, 2020.
  \item Program reviewer, Digital Humanities Conference 2019, ADHO Conference Coordinating Committee, Utrecht, Netherlands, 2019.
  \item Program reviewer, Digital Humanities Conference 2018, ADHO Conference Coordinating Committee, Mexico City, Mexico, 2018.
  \item Program reviewer, Digital Humanities Conference 2017, ADHO Conference Coordinating Committee, Montreal, Canada, 2017.
  \item Libraries and Digital Humanities Special Interest Group, 2017--2020.
\end{itemize}

\subsection*{Service to the Profession}

Referee for these journals, publishers, grant agencies, and academic software repositories: \textit{The Programming Historian}, \textit{The Public Historian}, \textit{Pacific Historical Review}, University of Michigan Press, National Endowment for the Humanities, Fonds National de la Recherche.

\vspace{.4cm}

\section{Departmental / College / University Service}

\subsection{University Committees}

\subsubsection*{University of Nebraska at Omaha}

\begin{itemize}
  \item Member, University Committee for the Advancement of Teaching, 2020--2021.
  \item Member, University Committee on Technology Resources, Services, and Planning, 2019--2021.
  \item Member, Sustainability Curriculum Committee, 2019--2021.
\end{itemize}

\subsection{College Committees}

\subsubsection*{George Mason University}

\begin{itemize}
  \item Member, System Administrator Search Committee, RRCHNM, 2022.
  \item Member, R2 Studios Producer Search Committee, RRCHNM, 2021.
  \item Member, R2 Studios Studio Administrator Search Committee, RRCHNM, 2021.
\end{itemize}

\subsubsection*{University of Nebraska at Omaha}

\begin{itemize}
  \item Member, Outreach Archivist Search Committee, UNO Libraries, 2019.
  \item Faculty Chair, Library Faculty, UNO Libraries, 2018--2019.
  \item Faculty Chair-Elect, Library Faculty, UNO Libraries, 2017--2018.
  \item Member, Social Science Librarian Search Committee, UNO Libraries, 2017.
  \item Organizer, Endangered Data Week, UNO Libraries, April 2017.
  \item Member, De-stress Fest Committee, UNO Libraries, 2017.
  \item Member, Triple Bottom Line Committee, UNO Libraries, 2017--2021 (Committee chair, 2017--2019).
\end{itemize}

\subsubsection*{Stanford University}

\begin{itemize}
  \item Member, Stanford Interactive Media Group, 2014--2016.
  \item Member, Stanford Interactive Mapping Group, 2013--2016.
  \item Member, Data Visualization Users Group, 2013--2016.
  \item Member, Stanford Mobile Users Group, 2014--2016.
\end{itemize}

\subsubsection*{South Dakota State University}

\begin{itemize}
  \item Secretary/Treasurer, Phi Alpha Theta, 2005--2006.
\end{itemize}

\subsection{Department Committees}

\textit{University of Nebraska at Omaha}

Member, OER Committee, 2018--2021.

\vspace{.4cm}

\textit{Stanford University}

Member, Digital Publishing Committee, Center for Spatial and Textual Analysis, 2013--2016.

Member, Digital Humanities Certificate Committee, Center for Spatial and Textual Analysis, 2013--2016.

Member, Stanford Network Analysis Group, Center for Spatial and Textual Analysis, 2015--2016.

\vspace{.4cm}

\textit{University of Nebraska-Lincoln}

Member, Digital Outreach Committee, History Graduate Students' Association, 2012--2013.

Co-Chair, Poster Committee, Center for Great Plains Studies Symposium, 2011--2012.

Vice President, History Graduate Students' Association, 2010--2011.

Assistant Director, Sixth Annual James A. Rawley Conference in the Humanities, 2010--2011.

Member, Program Committee, James A. Rawley Conference in the Humanities, 2009--2011.

Member, Digital Outreach Committee, History Graduate Students' Association, 2007--2010.

Executive Director, Fifth Annual James A. Rawley Conference in the Humanities, 2009--2010.

Chair, ad hoc Website Committee, History Graduate Students' Association, 2008--2009.

Treasurer, History Graduate Students' Association, 2008--2009.

Member, Publicity Committee, Third Annual James A. Rawley Conference in the Humanities, 2008--2009.

\subsection{University Service}

\textit{George Mason University}

Member, Data Working Group, Roy Rosenzweig Center for History and New Media, 2021--\textit{present}.

Member, Spatial History Working Group, Roy Rosenzweig Center for History and New Media, 2021--\textit{present}.

Member, Digital Public History Working Group, Roy Rosenzweig Center for History and New Media, 2021--\textit{present}.

\vspace{.4cm}

\textit{University of Nebraska at Omaha}

Organizer, Digital Humanities Community of Practice, UNO Libraries, 2018--2021.

Organizer, R User Group, UNO Libraries, 2019--2021.

Faculty Moderator, Student Research and Creative Activity Fair, University of
Nebraska at Omaha, March 2018, March 2019.

Member, Digital Engagement Community of Practice, UNO Libraries, 2017--2018.

\vspace{.4cm}

\textit{Stanford University}

Member, Spotlight Service Team, Center for Interdisciplinary Digital Research, 2016--2016.

Member, Stanford University Libraries Concierge Advisory Group, 2014--2016.

Member, Working Group on Stanford University Libraries Technical Infrastructure, 2013--2014.

\vspace{.4cm}

\textit{University of Nebraska-Lincoln}

Member, UNL Libraries Graduate Student Advisory Board, 2010--2012.

\subsection{Community Service}

\begin{itemize}
  \item Member, Environmental History Action Collaborative, Environmental Data \& Governance Initiative, 2020--\textit{present}.
  
  \item Deputy voter registrar, Douglas County, Nebraska, certified March 2018.
  
  \item Member, Mode Shift Omaha, Omaha, Nebraska, 2017--\textit{present}.
  
  \item Graduate Student Volunteer, History Harvest, Nebraska Public Television, University of Nebraska-Lincoln, Lincoln, Nebraska, 2010.
  
  \item Judge, National History Day, Nebraska State Competition, Nebraska Wesleyan University, Lincoln, Nebraska, 2009.
\end{itemize}

\subsection{Other Professional Service}

\begin{itemize}
  \item Member, Committee for Equity and Inclusion, Digital Library Federation, 2020--2021.
  
  \item Community Representative, Digital Public Library of America, 2017--2018.
  
  \item Member, Government Records Transparency and Accountability Group, Digital Library Federation, 2017--2020.
\end{itemize}

\end{document}
