Digital humanities scholar and developer with seven years of experience
in developing data science and digital publication solutions, consulting
and collaborating on project design and implementation, as well as
engaging in original research.

\section{Education}\label{education}

PhD in History, University of Nebraska-Lincoln (2016)\\
MA in History, University of Nebraska-Lincoln (2009)\\
BA in History, South Dakota State University (2007)

\section{Professional Experience}\label{professional-experience}

\textbf{Digital Engagement Librarian}, University of Nebraska at Omaha
Libraries (2017--\emph{present})

\textbf{Academic Technology Specialist},
\href{http://history.stanford.edu}{Department of History} and
\href{http://cidr.stanford.edu}{Center for Interdisciplinary Digital
Research} (CIDR), Stanford University (2013-2016)

\textbf{Research Staff}, \href{http://cesta.stanford.edu}{Center for
Spatial and Textual Analysis} (CESTA), Stanford University (2013-2016)

\textbf{Project Manager}, Center for Digital Research in the Humanities,
University of Nebraska-Lincoln (2011-2012)

\section{Select Projects}\label{select-projects}

\textbf{Research director}, \emph{\href{http://aidhp.com}{American
Indian Digital History Project}} (2016--\emph{present}). An Omeka
exhibit of material on American Indian history. Served as a technical
advisor in deciding on and setting up technical infrastructure, metadata
design, and document digitization. Primary investigator: Kent Blansett.

\textbf{Consultant}, \emph{\href{http://invisiblehistory.ops.org}{Making
Invisible Histories Visible}}, Omaha, Nebraska (2017--\emph{present}).
This program invites twenty-four high school freshmen from Omaha Public
Schools to take part in a summer program focused on the history of their
city. I serve as a consultant primarily on mapping and
digitally-interactive aspects of the projects produced in the program.

\textbf{Technical lead}, \emph{Chinese Railroad Workers in North
America}, Stanford University (2013--2016). Served as a technical
advisor and developer for a metadata management system, helped organized
and curate nearly 10,000 digitized objects, and trained sixteen research
assistants on metadata best practices and the platform used for
collecting metadata. Primary investigators: Gordon Chang and Shelley
Fischer Fishkin.

\textbf{Project manager}, \emph{\href{http://codyarchive.org}{William F.
Cody Archive}}, Center for Digital Research in the Humanities,
University of Nebraska-Lincoln (2011--2013). Supervised two graduate
student interns, maintained documentation on project milestones and
reference material, worked closely with museum staff at the Buffalo Bill
Center for the West, and helped organize nearly 24,000 digitized
documents.

\section{Select Publications}\label{select-publications}

\emph{Suburban by Nature: Silicon Valley and the Transformation of
American Environmental Politics}. Environment in Modern North America
series. Norman: University of Oklahoma Press, under contract.

\emph{Digital Community Engagement: Partnering Communities with the
Academy}. Co-editor with Rebecca Wingo and Paul Schaudenwald.
Cincinnati: University of Cincinnati Press, 2020.

Heidi Blackburn and Jason A. Heppler, ``Who is Writing about Women in
STEM in Higher Education? A Citation Analysis of Gendered Authorship,''
\emph{Frontiers in Psychology} 10 (2020).
\url{https://doi.org/10.3389/fpsyg.2019.02979}

Heidi Blackburn and Jason A. Heppler, ``Women in STEM in Higher
Education: A Citation Analysis of the Current Literature,''
\emph{Science \& Technology Libraries} (2019).
\url{https://doi.org/10.1080/0194262X.2019.1645080}

Brandon Locke and Jason A. Heppler, ``Teaching Data Literacy for Civic
Engagement: Resources for Data Capture and Organization,'' \emph{KULA:
Knowledge Creation, Dissemination, and Preservation Studies} 2 (1) (Fall
2018). \url{https://doi.org/10.5334/kula.23}

\section{Fellowships and Grants}\label{fellowships-and-grants}

Civic Participation Project, University of Nebraska at Omaha, 2020,
\$1,000.

Toward an Open Monograph Ecosystem (TOME), 2019, awarded, \$15,000.

Library of Congress Teaching with Primary Sources Grant, 2018, awarded,
\$19,750.

Eugene and Sunny Thomas Fund, UNO Libraries, 2018, \$5,500.

``Mobile Archives for Rural Communities,'' LYRASIS Catalyst Fund, 2017,
awarded, \$5,500.

\section{Computing Platforms and Digital
Humanities}\label{computing-platforms-and-digital-humanities}

Programming languages: R, Javascript, Python, Ruby, PHP, Unix shell
scripts

Data analysis: R (programming), D3.js (visualization), QGIS / ArcGIS
(mapping)

Data science: tidyverse, ggplot, Plotly

Versioning: SVN, Git, GitHub, GitLab

Web Frameworks/Content Management Systems: WordPress, Jekyll, Omeka,
Drupal

Operating Systems: Linux, MacOS, Windows, VMS

Database Systems/Persistence: MySQL, SQLite, Postgres

Web/Markup Languages: XML, JSON, HTML, CSS, XSLT 1.0 and 2.0, TEI,
\LaTeX

Systems Administration: Linux, Apache, MySQL

Applications: Microsoft Office, Adobe Photoshop, Adobe Illustrator

\section{Languages}\label{languages}

English (native proficiency), Norwegian (beginner proficiency)
