\section{Education}\label{education}

\textbf{Ph.D.}, History, University of Nebraska-Lincoln (2016)\\
\textbf{M.A.}, History, University of Nebraska-Lincoln (2009)\\
\textbf{B.A.}, History, South Dakota State University (2007)

\section{Appointments}\label{appointments}

Senior Developer, Roy Rosenzweig Center for History and New Media,
George Mason University (2021--present)

Adjunct Assistant Professor, Department of History and Art History,
George Mason University (2024--present)

\section{Major Affiliations and
Fellowships}\label{major-affiliations-and-fellowships}

Affiliate Scholar, Connecting the Interstates, NEH ODH Planning Grant
(2020--present)

Member, Environmental History Action Collaboratory (2020--present)

\section{Editorial and Advisory
Appointments}\label{editorial-and-advisory-appointments}

Advisory Board, Open Online Newspaper Initiative (2022--present)

Advisory Board, Sourcery (2021--present)

\newpage

\section{Selected Publications}\label{selected-publications}

\emph{Silicon Valley and the Environmental Inequalities of High-Tech
Urbanism}. Norman: University of Oklahoma Press, 2024.

\emph{Digital Community Engagement: Partnering Communities with the
Academy}. Co-editor with Rebecca Wingo and Paul Schadewald. Cincinnati:
University of Cincinnati Press, 2020. (Awarded the National Council on
Public History Book Award, 2021).

``Green Dreams, Toxic Legacies: Toward a Digital Political Ecology of
Silicon Valley,'' \emph{International Journal of Humanities and Arts
Computing}, vol.~11, no. 1 (March 2017): 68--85.

\section{Selected Presentations}\label{selected-presentations}

``History and the Spatial Turn: Pedagogical Approaches,'' round table
discussant, at the 136th American Historical Association, January 2023,
Philadelphia, Pennsylvania.

``Space, Time, and Visualizing the London Bills of Mortality,'' Southern
History Association, November 11, 2022, Baltimore, Maryland.

``Digitizing and Transcribing the 1926 Census of Religious Bodies,''
Society for the Scientific Study of Religion and the Religious Research
Association, November 11-13, 2022, Baltimore, Maryland.

``\,`As the people came, the orchards went': Water, Energy, and Land in
Silicon Valley, 1945-1970,'' Annual Meeting of the Agricultural History
Society, August 2022, Stavanger, Norway.

\section{Select Collaborative Digital
Projects}\label{select-collaborative-digital-projects}

\emph{Connecting Threads}, Roy Rosenzweig Center for History and New
Media, George Mason University (in progress, 2022--):
https:connectingthreads.co.uk. (co-PI)

\emph{Death by Numbers}, Roy Rosenzweig Center for History and New
Media, George Mason University (in progress, 2021--):
https://deathbynumbers.org. (senior developer)

\emph{American Religious Ecologies}, Roy Rosenzweig Center for History
and New Media, George Mason University (in progress, 2018--):
https://religiousecologies.org. (senior developer)

\emph{American Indian Digital History Project} (in progress, 2017--):
http://aidhp.com (research director)

\section{Other Academic Publications}\label{other-academic-publications}

Molly Taylor-Polesky and Jason Heppler, ``The 1613 Marriage Journey of
Elizabeth Stuart: Reflections on Visualizing European Geopolitics on the
Brink of the Thirty Years War,'' Spatial History Project, Stanford
University, June 20, 2018:
\url{https://web.stanford.edu/group/spatialhistory/cgi-bin/site/pub.php?id=129}.

Arguing with Digital History working group, ``Digital History and
Argument,'' white paper, Roy Rosenzweig Center for History and New
Media, George Mason University, November 13, 2017:
\textless http://rrchnm. org/argument-white-paper/\textgreater.
